Chapter 12 Graphs
=================================================
This report creates the chapter graphs.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of only one directory.-->
```{r, echo=TRUE, message=F} 
opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=TRUE}
require(knitr)
opts_chunk$set(
    results='show', 
    comment = NA, 
    tidy = FALSE,
    fig.width = 5.5, 
    fig.height = 4, 
    out.width = "600px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
    fig.path = 'figure_rmd/',     
    dev = "png",
    dpi = 400
    #dev = "pdf"
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./Chapter12/Chapter12.R") 
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets. -->
```{r LoadDatasets, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets. -->
```{r TweakDatasets, echo=echoChunks, results='show', message=FALSE}
```

## Figure 12-1
Consider if you want the publisher to construct this as a table, but still label it as a figure.  It will be easier to have the size and fonts match the text.  ...Lise's response: Agreed.  I can set it up in Word and let them deal with it.

## Figure 12-2
These are separate images.

```{r Figure12_02, echo=echoChunks, results='show', message=TRUE, out.width = "400px", fig.width = 4}
```

## Figure 12-3
```{r Figure12_03, echo=echoChunks, results='show', message=TRUE, out.width = "800px", fig.width = 7.5}
```

## Figure 12-4
```{r Figure12_04, echo=echoChunks, results='show', message=TRUE}
```

## Figure 12-5
Table of Critical *F* values.  Will be produced by publisher.

## Figure 12-6
```{r Figure12_06, echo=echoChunks, results='show', message=TRUE}
```

## Figure 12-7
```{r Figure12_07, echo=echoChunks, results='show', message=TRUE, out.width = "600px", fig.width = 5}
```

## Figure 12-8 through 12-11
```{r Figure12_08, echo=echoChunks, results='show', message=TRUE}
```

## Figure 12-12
```{r Figure12_12, echo=echoChunks, results='show', message=TRUE, fig.width=3.0, fig.height=2.0, out.width="350px"}
```

## Figure 12-13
```{r Figure12_13, echo=echoChunks, results='show', message=TRUE}
```
Lise, let's talk about this one on the phone before I get into it.



## Session Info
For the sake of documentation and reproducibility, the current report was build on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report created by", Sys.info()["user"], "at", strftime(Sys.time(), "%F, %T %z"))
sessionInfo()
```
